---
title: "Simple Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simple Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(details)
```

```{r setup}
library(reactor)
```

## Simple App

### Good App

In this app the plot is only rendered when the `input$n` is updated. 

- We expect the reactive element that creates the plot to be invalidated only once.

```{details,echo = FALSE,details.summary  = 'Good App Script',details.open = TRUE}
system.file('examples/good_app.R',package = 'reactor')
```

### Bad App

In this app the plot is rendered every time reactive elements in `input` are invalidated. 

  - This kind of setup can cause a lot of unwanted reactivity in larger apps with many elements.
  - We expect the reactive element that creates the plot to be invalidated more than once.
  - Notice how on the app initialization the chunk is rendered twice. 

```{details,echo = FALSE,details.summary = 'Bad App Script',details.open = TRUE}
system.file('examples/bad_app.R',package = 'reactor')
```

### Testing

Using `reactor` we can test this expectation!

If we run the test on the `good app` the test will pass and if we run it on the `bad app` then it will fail signaling a problem.

To run a test you can use standard `testthat` functions like `testthat::test_dir()`, or you can use a `reactor` function `reactor::test_app()`. 

To use `test_app` just name the test file `reactor-*.R` instead of `test-*.R` this will have two benefits.

  1. `covr` will not pass the tests. This allows you to run the tests using `test_dir` which does have the necessary characteristics to run the tests.
  2. Allows the app tests to be isolated from the other unit tests thus allowing for `covr` and `testthat` to run on R CMD CHECK without needing to add `skip_*` into the app test files.


```{details,echo = FALSE,details.summary = 'Reactivity Test Script',details.open = TRUE}
'../tests/testthat/reactor-rselenium.R'
```
